\added{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}

### 2025-02-14 main.tex
Intro, con. & fig caps

\begin{itemize}
%   \item Novel deep learning pipeline for automated 3D grape phenotyping.
%   \item GrapeCPNet: Self-supervised network for berry points cloud completion.
%   \item High accuracy in berry instance segmentation (99.5\% average precision).
%   \item Robust performance across four grape varieties ($R^2$ of 0.855 for radius, 0.969 for 
% volume).
%   \item Nondestructive and highthroughput analysis for viticulture applications.
  \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
  \item \added{GrapeCPNet is trained using self-supervision, free of manual annotations.}
  \item \added{Integrated into a deep learning pipeline for automated 3D grape bunch phenotyping.}
  \item \added{Achieved over 0.85 $R^2$ and 99.5\% average precision on four grape varieties.}
\end{itemize}

@@

\section{Introduction}
Fresh grape is one of the most important agricultural products and economic crops \citep{alston_grapes_2019}. 
Its global production and consumption is increasing year by year. 
To better guide planting strategy and monitoring growing status, several geometric parameters like counts, length, and volume at bunch level and berry level are commonly used in actual applications. \citep{luo_prediction_2024,raihen_prediction_2024}. 
Among them, the number and the radius of the berries are the most important phenotypic parameters \citep{sneha_acrescale_2024}. 
Traditional manual phenotyping of traits is labor-intensive and time-consuming, and often destructive. 
To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic traits based on computer vision has attracted extensive interest in recent years. 
Several simple geometry traits can be acquired from 2D images by using computer vision algorithms that use pattern recognition, machine learning, and deep learning \citep{zabawa_counting_2020}. 
Projecting the 2D image plane onto the 3D world inevitably results in information loss. 
The occlusion of berries often lead to incomplete representations of grape bunches. 
Additionally, clustered berries and their shadows  create challenges for obtaining reliable measurements of phenotypic parameters through 2D image analysis, even under controlled lightning conditions  \citep{fei_comprehensive_2022,xiang_multispace_2023}.

Advances in 3D scanning and reconstruction techniques have made it possible to retain detailed spatial information about objects, enabling the acquisition of complex 3D morphological traits in grape bunches \citep{jiang_3d_2019,ni_threedimensional_2021}. 
Researchers have developed 3D phenotyping processes for grapes by combining feature-engineered point cloud processing algorithms \citep{rose_automated_2016,rist_highprecision_2018}. 
These methods primarily rely on point cloud segmentation techniques, such as edge-based segmentation, region-growing segmentation, and sphere-fitting algorithms. 
Unfortunately, traditional point cloud processing algorithms heavily rely on prior knowledge of the target object and require extensive manual feature engineering and parameter tuning to achieve optimal results in a wide range of conditions, thereby limiting their generalization performance.
\added{Implementing} state-of-the-art deep learning approaches\replaced{, which automatically learn features}{use a data-driven feature learning} from the point cloud data \replaced{, can  reduce the workload of designing robust algorithms for complex and diverse conditions}{ automatically}.
\deleted{It recently shows promising adaptability and accuracy in plant 3D phenotyping (schneider\_predicting\_2020, scholer\_automated\_2015). }
\deleted{Focusing on point cloud segmentation applications, }
\deleted{li\_maspc\_2022 proposed MASPC\_Transform to segment the stems and leaves of rose bush point cloud data to obtain 3D phenotypic parameters. }
\deleted{wang\_3d\_2022 realized leaf instance segmentation by designing the PartNet for lettuce point cloud data. }
\deleted{li\_psegnet\_2022 proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. }
\replaced{However, few studies have reported deep learning networks perform well in}{The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on} berry level analysis.

@@

\subsection{Berry Instance Segmentation \added{Module}}
\label{sec:22}

@@

\subsection{Self-Supervised Point Cloud Completion \added{Module}}

@@

To validate the accuracy of extracted morphological traits, the 12 validation bunches  were used after instance berry segmentation and berry completion (refer to Section~\ref{sec:22}). 
The radius and volume of the 108 samples were calculated. 
For ground truth measurement, we used the values of the radius and volume of the individual complete berry from the completed point clouds.

@@

To verify the efficiency of GrapeCPNet, we compared it to other point cloud completion networks: PoinTr, SnowFlakeNet, TopNet \citep{tchapmi_topnet_2019}, and GRNet \citep{xie_grnet_2020}.

@@

% figure 17
\begin{figure}[hbt!]
    \centering
    \includegraphics[width=1\textwidth]{figures/Figure14.pdf}
    \caption{Experimental results of axis length calculation for four species of fresh grape. From (a)-(d): Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape, and from (1)-(3): the calculation of the long, middle, and short axis, respectively.}
    \label{fig:raw17}
\end{figure}

@@

% figure 18
\begin{figure}[hbt!]
    \centering
    \includegraphics[width=1\textwidth]{figures/Figure15.pdf}
    \caption{Experimental results of berry volume calculation.}
    \label{fig:raw18}
\end{figure}

@@

\section{Discussion and Conclusion}

@@

aaa

>>>>

\begin{itemize}
%   \item Novel deep learning pipeline for automated 3D grape phenotyping.
%   \item GrapeCPNet: Self-supervised network for berry points cloud completion.
%   \item High accuracy in berry instance segmentation (99.5\% average precision).
%   \item Robust performance across four grape varieties ($R^2$ of 0.855 for radius, 0.969 for 
% volume).
%   \item Non-destructive and high-throughput analysis for viticulture applications.
  \item \added{GrapeCPNet completes 3D point clouds for segmented berry instances.}
  \item \added{GrapeCPNet is trained using self-supervision, free of manual annotations.}
  \item \added{Integrated into a deep learning pipeline for automated 3D grape bunch phenotyping.}
  \item \added{Achieved over 0.85 $R^2$ and 99.5\% average precision on four grape varieties.}
\end{itemize}

@@

\section{Introduction}
Fresh grape is one of the most important agricultural products and economic crops \citep{alston_grapes_2019}. 
Its global production and consumption is increasing year by year. 
To \replaced{effectively}{better} guide planting strategies and monitoring growing status, several geometric parameters\replaced{, including}{like counts, length, and volume at bunch level and berry level are commonly used in actual applications raihen\_prediction\_2024.} 
\deleted{Among them,} the number \deleted{and the radius }of \deleted{the} berries \replaced{and their radius, are frequently measured}{are the most important phenotypic parameters (sneha\_acrescale\_2024) }. 
Traditional manual \replaced{measuring}{phenotyping of }traits is labor-intensive and time-consuming, and often destructive. 
To reduce the cost and increase the efficiency, the non-destructive and high-throughput acquisition of phenotypic traits based on computer vision has attracted extensive interest in recent years. 
Several simple geometry traits can be acquired from 2D images by using computer vision algorithms that use pattern recognition, machine learning, and deep learning \citep{chen_instance_2023, zabawa_counting_2020}. 
Projecting the 2D image plane onto the 3D world inevitably results in information loss. 
The occlusion of berries often lead to incomplete representations of grape bunches. 
Additionally, clustered berries and their shadows create challenges for obtaining reliable measurements of phenotypic parameters through 2D image analysis, even under controlled lightning conditions.

Advances in 3D scanning and reconstruction techniques have made it possible to retain detailed spatial information about objects, enabling the acquisition of complex 3D morphological traits in grape bunches \citep{ni_threedimensional_2021}. 
Researchers have developed 3D phenotyping processes for grapes by combining feature-engineered point cloud processing algorithms \citep{rose_automated_2016, rist_highprecision_2018}. 
These methods primarily rely on point cloud segmentation techniques, such as edge-based segmentation, region-growing segmentation, and sphere-fitting algorithms. 
Unfortunately, traditional point cloud processing algorithms heavily rely on prior knowledge of the target object and require extensive manual feature engineering and parameter tuning to achieve optimal results in a wide range of conditions, thereby limiting their generalization performance.
\added{Implementing} state-of-the-art deep learning approaches\replaced{, which automatically learn features}{use a data-driven feature learning} from the point cloud data \replaced{, can  reduce the workload of designing robust algorithms for complex and diverse conditions}{ automatically}.
\deleted{It recently shows promising adaptability and accuracy in plant 3D phenotyping (schneider\_predicting\_2020, scholer\_automated\_2015). }
\deleted{Focusing on point cloud segmentation applications, }
\deleted{li\_maspc\_2022 proposed MASPC\_Transform to segment the stems and leaves of rose bush point cloud data to obtain 3D phenotypic parameters. }
\deleted{wang\_3d\_2022 realized leaf instance segmentation by designing the PartNet for lettuce point cloud data. }
\deleted{li\_psegnet\_2022 proposed PSegNet for segmenting stems and leaves of tomato, tobacco, and sorghum. }
\replaced{However, few studies have reported good performance deep learning networks in}{The previous studies focused on canopy level or individual plant level analysis, and demonstrated that instance segmentation alone is insufficient on} berry level analysis.

@@

\subsection{Berry Instance Segmentation}
\label{sec:22}

@@

\subsection{Self-Supervised Point Cloud Completion}

@@

To validate the accuracy of extracted morphological traits, the 12 validation bunches \added{with 108 berry samples} were \replaced{selected. The berries were first scanned while still attached to bunch (Fig.~\ref{fig:raw9}a2). After instance segmentation, these scans of each berry are incomplete caused by occlusion. We then applied our proposed self-supervised completion method to get completion predictions. Finally get ellipsoidal surface fitting results as prediction values. }{ used after instance berry segmentation and berry completion (refer to Section~\ref{sec:22})} 
\deleted{The radius and volume of the 108 samples were calculated.} 
For ground truth measurement, \replaced{we separated berries from the bunch to get complete scans of corresponding berry (Fig.~\ref{fig:raw9}b1). Then applied the ellipsoidal surface fitting to these completely scans. }{we used the values of the radius and volume of the individual complete berry from the completed point clouds.}

@@

To verify the efficiency of GrapeCPNet, we compared it to other point cloud completion networks: PoinTr \citep{yu_pointr_2021} SnowFlakeNet \citep{xiang_snowflakenet_2021}, TopNet \citep{tchapmi_topnet_2019}, and GRNet \citep{xie_grnet_2020}.

@@

% figure 17
\begin{figure}[hbt!]
    \centering
    \includegraphics[width=1\textwidth]{figures/Figure14.pdf}
    \caption{Experimental results of axis length calculation for four species of fresh grape. From (a)-(d): Red Grape, Green Grape, Kyoho Grape, and Shine-Muscat Grape, \deleted{and from (1)-(3): the calculation of the long, middle, and short axis, }respectively. \added{The ground truth values are obtained by completely scanning berries that were separated from the bunch (Fig.~\ref{fig:raw9}b1); The predicted values are obtained from our proposed self-supervised completion method, which addresses incomplete scans of berries that occur due to occlusion while they were still attached to the bunch (Fig.~\ref{fig:raw9}a2).}}
    \label{fig:raw17}
\end{figure}

@@

% figure 18
\begin{figure}[hbt!]
    \centering
    \includegraphics[width=1\textwidth]{figures/Figure15.pdf}
    \caption{Experimental results of berry volume calculation. \added{The ground truth values are obtained by completely scanning berries that were separated from the bunch (Fig.~\ref{fig:raw9}b1); The predicted values are obtained from our proposed self-supervised completion method, which addresses incomplete scans of berries that occur due to occlusion while they were still attached to the bunch (Fig.~\ref{fig:raw9}a2).}}
    \label{fig:raw18}
\end{figure}

@@

\section{Discussion}

\added{}

@@

\added{In this study, we proposed a deep-learning-based pipeline for processing 3D phenotyping grape bunches reconstructed by photogrammetry.}
\added{The major contribution is the self-supervised completion network, named GrapeCPNet, designed to address the problem of missing parts in berries occluded within grape bunches with few manual annotations.}
\added{Due to the dense and compact arrangement of berries within a grape bunch, the inner portions are often occluded and not visible.}
\added{This often presents challenges in algorithm design for individual berry segmentation and accurate berry size estimation.}
\added{We utilized state-of-the-art, data-driven deep learning approaches to address these challenges.}
\added{First, the SoftGroup network, utilizing segmentation annotations from 8 grape bunches, was used to train a data-driven berry instance segmentation model.}
\added{By randomly producing missing areas from complete berries, we automatically generated large number of training data for completion tasks.}
\added{By combining the centroid-based sparsed completion and diffusion-based dense completion structure, the proposed GrapeCPNet achieved better performance than existing completion networks, with Precision of 0.729, Recall of 0.772 and F-score of 0.751.}
\added{The ellipsoid surface fitting, used to calculate three axis lengths and volumes, achieved an average $R^2$ of 0.86 and 0.97 respectively, when comparing completed berries with their ground truth.}
\added{This study clearly demonstrates the potential of using data-drive strategies with minimal annotation effort to address the 3D occlsuion challenge in agricultural applications.}
\added{Although this network has only been tested on grape bunches collected in a controlled environment, the proposed deep learning pipelines and training data generation approach have broad potential applications for in-field vineyards and even other crops in the future.}
